pairwise plot of flash result of flash Z-score

### 2017-05-01 analysis/pairwiseplotofflashgtexzscore.Rmd
Files commited by wflow_commit.

```{r}
plot(b_flash$l[,1],b_flash$l[,3],col = as.vector(colordata[,2]),pch = 16)
text(b_flash$l[,1],b_flash$l[,3], labels=colordata[,1], cex= 0.7)
```

>>>>

```{r}
i = 1
j = 3
plot(b_flash$l[,i],b_flash$l[,j],col = as.vector(colordata[,2]),pch = 16)
text(b_flash$l[,i],b_flash$l[,j], labels=colordata[,1], cex= 0.7)
```
